---
title: "Amandafwu_OriginalHomeworkCode_02"
author: "Amanda Wu"
date: "2023-09-28"
output: html_document
---
## Prompt
### Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

### What is the probability that she will hear more than 8 calls during any given session?
```{r Question 1}
x <- 0:8
l <- 15
probset <- 1 - dpois(x, lambda = l)
probset
```


### What's the probability that she will hear no calls in one session?
```{r Question 2}
x <- 0
l <- 15
probset <- dpois(x, lambda = l)
probset
hist(probset, breaks = c(0:30), probability = TRUE, main = "No Calls", xlab = "# of calls", ylab = "probability")

```


### What is the probability that she will hear exactly 3 calls in a session?
```{r Question 3}
x <- 3
l <- 15
probset <- dpois(x, lambda = l)
probset
```


### Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r Question 4}
x <- 0:30
l <- 15
probset <- dpois(x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")
```


### Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions). 
```{r Question 5}

```





